\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2020-04-06 gwnnDraft02.tex
Fixed equation reference and typos.

If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{v}$ components \citep{Breitbach:2018ddu},
\begin{equation}\label{eqn:Spectralnonrun}
h^2\Omega_{\textrm{GW}} \approx  h^2\Omega_{v} + h^2\Omega_{turb}.
\end{equation}

@@

In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component. For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time. When estimating the model expectations for $\beta/H = 10^4$, we enter a regime at which Eq.~(\ref{eqn::SNR}) \draftnote{Is this the right equation reference?} may be overestimating the sound wave contribution. Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}. This effect, however, only affects the amplitude of the signal, and our work focuses on the unique spectral shapes that are formed in these models. Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw} to motivate the novel spectral profiles.

>>>>

If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{turb}$ components \citep{Breitbach:2018ddu},
\begin{equation}\label{eqn:Spectralnonrun}
h^2\Omega_{\textrm{GW}} \approx  h^2\Omega_{v} + h^2\Omega_{turb}.
\end{equation}

@@

In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component. For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time. When estimating the model expectations for $\beta/H = 10^4$, we enter a regime at which Eq.~(\ref{eqn::SWMHD}) may be overestimating the sound wave contribution. Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}. This effect, however, only affects the amplitude of the signal, and our work focuses on the unique spectral shapes that are formed in these models. Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw} to motivate the novel spectral profiles.
